The effects of binarity on planet occurrence rates measured by transit surveys

### 2017-11-09 paper/figures.tex
fig1: update caption

\newpage
\begin{figure}
    \begin{center}
        \includegraphics[width=\textwidth]{figures/visualize_volumes.pdf}
    \end{center}
    \caption{
    Cartoon of the different selected and searchable volumes for single 
    stars (left column), and twin binaries (right column).
    This model (\#1) assumes all stars have equal mass and luminosity.
    Since the observer does not recognize the brighter binaries, they select 
    them out to a larger distance, $\sqrt{2}\times$ that of single stars.
    However, dilution causes the twin binaries to only be searchable in one 
    eighth of their selected volume.
    }
    \label{fig:model_1_volumes}
\end{figure}

>>>>

\newpage
\begin{figure}
    \begin{center}
        \includegraphics[width=\textwidth]{figures/visualize_volumes.pdf}
    \end{center}
    \caption{
    In Model \#1, we assume all stars have equal mass and luminosity, and that 
    the observer cannot resolve binary systems.
    For single stars (left), at fixed planet size and period, the 
    selected and searchable volumes are then identical.
    Twin binaries (right) are twice as luminous, and so are selected 
    out to a maximum distance $\sqrt{2}\times$ that of single stars 
    (Eq.~\ref{eq:d_sel}).
    However, the diluting light from the twin companion lowers the maximum 
    distance at which a planet can be detected, relative to single stars, by 
    $1/\sqrt{2}$ (Eq.~\ref{eq:d_det_i}).
    }
    \label{fig:model_1_volumes}
\end{figure}
